Investigating social change during cultural contact period using geometric morphometry of pottery shapes from Iron Age northeastern Taiwan

### 2019-12-22 analysis/paper/paper.Rmd
add references

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)
```

@@

The elliptic Fourier coefficients of `r total_no` pottery from three different phases were calculated. Reliable pottery outline was captured by 13 harmonics that gather 99 % of the total harmonic power. Thin-plate splines compares the average shapes of vessels from each period to visualize the outline deformations required to pass from an extreme of one morphospace to the other.

The mean petal shape of each variety was then drawn using the mean values of the standardized Fourier coefficients within each variety. Figure 1 shows the wide variation of petal shape that was observed among the varieties examined in this study.

@@

```{r EFA-analysis}
library(Momocs)
jpgs_imported_coo <- readr::read_rds(here::here("analysis/data/derived_data/jpgs_imported_coo.rds"))

@@

# Thin plate spline analysis (TPS)
# Thin plate splines (TPS) was used to compare average shapes and visualise the outline deformations required to pass from an extreme of the morphospace to the other.
# Deformation grids
png(here::here("analysis/figures/tps-pre-Euro-to-post-Euro.png"), res = 300, w = 900, h = 900)

@@

png(here::here("analysis/figures/tps-pre-Euro-to-Chinese.png"), res = 300, w = 900, h = 900)
tps_grid(`Pre-European`, `Chinese`, shp.lwd = c(2, 2), shp.border = c("red", "blue"),
         amp = 1, grid.size = 18, legend = T)
dev.off()

# Isodeformation lines
png(here::here("analysis/figures/tps-iso.png"), res = 600, w = 1200, h = 1800)
tps_iso(`Pre-European`, `Post-European`,  shp.lwd = c(2, 2), shp.border = c("red", "blue"),
        amp = 0.5, iso.nb = 10000, iso.levels = 12, legend.text = c("Pre-contact", "Post-contact"),
        palette = col_summer, grid = F)
dev.off()
```

>>>>

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  dpi = 300,
  fig.path = "../figures/"
)
```

@@

@@

The elliptic Fourier coefficients of `r total_no` pottery from three phases were calculated. Reliable pottery outline was captured by 13 harmonics that gather 99 % of the total harmonic power. The mean pottery shape of each phase was visualized by calculating the mean of the standardized Fourier coefficients within each group. 
Thin-plate splines compares the average shapes of vessels from each period to visualize the outline deformations required to pass from an extreme of one morphospace to the other.

```{r EFA-analysis}
library(Momocs)
library(cowplot)
jpgs_imported_coo <- readr::read_rds(here::here("analysis/data/derived_data/jpgs_imported_coo.rds"))

@@

# Thin plate spline analysis (TPS)
# Thin plate splines (TPS) was used to compare average shapes and visualise the outline deformations required to pass from an extreme of the morphospace to the other.
# Deformation grids

@@

tps_grid(`Pre-European`, `Chinese`, shp.lwd = c(2, 2), shp.border = c("red", "blue"),
         amp = 1, grid.size = 18, legend = T)
dev.off()

# Isodeformation lines
png(here::here("analysis/figures/tps-iso.png"), res = 600, w = 1200, h = 1800)
de_pre_post_plot <- 
  tps_iso(`Pre-European`, `Post-European`,  shp.lwd = c(2, 2), shp.border = c("red", "blue"),
          amp = 0.5, iso.nb = 10000, iso.levels = 12, legend.text = c("Pre-contact", "Post-contact"),
          palette = col_summer, grid = F)
dev.off()

de_pre_chi_plot <- 
  tps_iso(`Pre-European`, `Chinese`,  shp.lwd = c(2, 2), shp.border = c("red", "blue"),
          amp = 0.5, iso.nb = 10000, iso.levels = 12, legend.text = c("Pre-contact", "Chinese"),
          palette = col_summer, grid = F)
dev.off()

# Doesn't work if the plot is not produced by ggplot?
# plot_two_de_by_period <- 
  #plot_grid(de_pre_post_plot, de_pre_chi_plot, labels = c('A', 'B'))

#knitr::include_graphics(here::here("analysis", "figures", "tps-pre-Euro-to-post-Euro.png"))
#knitr::include_graphics(here::here("analysis", "figures", "tps-pre-Euro-to-Chinese.png"))
